Biden Expected to Win 54% of Popular Vote in 2020 US Presidential Election

### 2020-11-03 outputs/paper/paper.Rmd
s

```{r, echo=FALSE}
cell_counts <- readRDS("../../inputs/cell_counts.RDS")
training_data <- readRDS("../../inputs/training_data.RDA")
model <- readRDS("../../model/4chains_3000iter_.rds")

@@

# Appendix {-}

>>>>

```{r, echo=FALSE}
#load pre preprocessed items, created through the scripts
cell_counts <- readRDS("../../inputs/cell_counts.RDS")
training_data <- readRDS("../../inputs/training_data.RDA")
model <- readRDS("../../model/4chains_3000iter_.rds")

@@
